### 2016-09-20 R/ITHIM.Rmd
Worked on Figures for Manuscript #1
Also updated the Make file in the top-level directory.  make all runs the whole thing now with dependencies in place.

```{r ITHIMObjs, eval = TRUE, fig.width = 20, fig.height = 10, echo = FALSE, warning = FALSE}
compute <- TRUE

if(compute){

DALYsTotal <- data.frame()

for( muNonTravel in seq(1,50,length.out = 20) ){

  ITHIMList <- list()
  rm(DALYs)
  ITHIM.default <- createITHIM(vision = "baseline", region = "national")

  for (HHS in c(paste0("HHS0",1:9),"HHS10")){
    ITHIMList[[HHS]] <- ITHIM.default
    ITHIMList[[HHS]] <- updateITHIM(ITHIMList[[HHS]], "muwt", muwtList[[HHS]])
    ITHIMList[[HHS]] <- updateITHIM(ITHIMList[[HHS]], "muct", muctList[[HHS]])
    ITHIMList[[HHS]] <- updateITHIM(ITHIMList[[HHS]], "Rwt", RwtList[[HHS]])
    ITHIMList[[HHS]] <- updateITHIM(ITHIMList[[HHS]], "Rct", RctList[[HHS]])
    ITHIMList[[HHS]] <- updateITHIM(ITHIMList[[HHS]], "GBD", GBDList[[HHS]])
    ITHIMList[[HHS]] <- updateITHIM(ITHIMList[[HHS]], "muNonTravel", muNonTravel)
  }

  ITHIM.national <- createITHIM(vision = "baseline", region = "national")
  ITHIM.national <- updateITHIM(ITHIM.national, "muNonTravel", muNonTravel)
  ITHIM.national <- updateITHIM(ITHIM.national, "muwt", muwtNational)
  ITHIM.national <- updateITHIM(ITHIM.national, "muct", muctNational)
  ITHIM.national <- updateITHIM(ITHIM.national, "Rwt", RwtNational)
  ITHIM.national <- updateITHIM(ITHIM.national, "Rct", RctNational)
  DALYs <- lapply(ITHIMList, sumDALY, ITHIM.baseline = ITHIM.national)
  DALYs <- data.frame(HHS = names(DALYs), muNonTravel = muNonTravel, DALY = unlist(DALYs))
  DALYsTotal <- rbind(DALYsTotal, DALYs)
}

}else{
  DALYsTotal <- readRDS(file = "./data/DALYsTotal.rds")
}

barplot(with(NHTS,table(HHS)))
p <- ggplot(DALYsTotal, aes(x = muNonTravel, y = DALY, colour = HHS))
p  + geom_line(size = 2) + theme_bw() + scale_x_continuous(name="Non-Travel METs mean") + scale_y_continuous(name="Change in DALY (National)") + facet_grid(. ~ HHS)
```

@@

```{r meanMatrices, eval = TRUE, fig.width = 20, fig.height = 10, warning = FALSE, message = FALSE, echo = FALSE}

@@

D <- melt(c(meanMatrixListWalk,meanMatrixListCycle))

names(D) <- c("ageClass", "mode", "sex", "time", "HHS")

#D <- within(D, HHS <- factor(HHS, levels = c(paste0("HHS",1:10),"Natl")))

p1 <- ggplot(D, aes(x = ageClass, y = time, fill = sex)) + geom_bar(stat= "identity", position = "dodge") + facet_grid( mode ~ HHS, scales = "free_y")

p1

>>>>

```{r ITHIMObjs, eval = TRUE, fig.width = 8, fig.height = 5, echo = FALSE, warning = FALSE}
upper <- 8
length <- 100

DALYsTotal <- data.frame()
ITHIMList <- list()
ITHIM.default <- createITHIM(vision = "baseline", region = "national")

for (HHS in c(paste0("HHS0",1:9),"HHS10")){
    ITHIMList[[HHS]] <- ITHIM.default
    ITHIMList[[HHS]] <- updateITHIM(ITHIMList[[HHS]], "muwt", muwtList[[HHS]])
    ITHIMList[[HHS]] <- updateITHIM(ITHIMList[[HHS]], "muct", muctList[[HHS]])
    ITHIMList[[HHS]] <- updateITHIM(ITHIMList[[HHS]], "Rwt", RwtList[[HHS]])
    ITHIMList[[HHS]] <- updateITHIM(ITHIMList[[HHS]], "Rct", RctList[[HHS]])
    ITHIMList[[HHS]] <- updateITHIM(ITHIMList[[HHS]], "GBD", GBDList[[HHS]])
  }

ITHIM.national <- createITHIM(vision = "baseline", region = "national")
ITHIM.national <- updateITHIM(ITHIM.national, "muwt", muwtNational)
ITHIM.national <- updateITHIM(ITHIM.national, "muct", muctNational)
ITHIM.national <- updateITHIM(ITHIM.national, "Rwt", RwtNational)
ITHIM.national <- updateITHIM(ITHIM.national, "Rct", RctNational)

for( muNonTravel in seq(0.01,upper,length.out = length) ){

  rm(DALYs)

  for (HHS in c(paste0("HHS0",1:9),"HHS10")){
    ITHIMList[[HHS]] <- updateITHIM(ITHIMList[[HHS]], "muNonTravel", muNonTravel)
  }

  ITHIM.national <- updateITHIM(ITHIM.national, "muNonTravel", muNonTravel)

  DALYs <- lapply(ITHIMList, sumDALY, ITHIM.baseline = ITHIM.national)
  DALYs <- data.frame(HHS = names(DALYs), muNonTravel = muNonTravel, DALY = unlist(DALYs))
  DALYsTotal <- rbind(DALYsTotal, DALYs)
}

barplot(with(NHTS,table(HHS)))

p <- ggplot(DALYsTotal, aes(x = muNonTravel, y = DALY/1e3, colour = HHS))

p + stat_smooth( method = loess) + theme_bw() + scale_x_continuous(name="Non-Travel METs mean (MET-hrs./week)") + scale_y_continuous(name="Change in National DALYs (Thousands)") + coord_cartesian(xlim = c(0, upper))

p + stat_smooth( method = loess) + theme_bw() + scale_x_continuous(name="Non-Travel METs mean (MET-hrs./week)") + scale_y_continuous(name="Change in National DALYs (Thousands)") + coord_cartesian(xlim = c(0, upper)) + geom_point()

@@

```{r meanMatrices, eval = TRUE, fig.width = 10, fig.height = 5, warning = FALSE, message = FALSE, echo = FALSE}

@@

D <- melt(c(meanMatrixListWalk,meanMatrixListCycle))
names(D) <- c("ageClass", "mode", "sex", "time", "HHS")

p1 <- ggplot(D, aes(x = ageClass, y = time, fill = sex)) + geom_bar(stat= "identity", position = "dodge") 
p1 + theme_bw() + scale_x_discrete(name="Age Class", breaks = c(2,4,6,8)) + scale_y_continuous(name="Travel Minutes per Week") + facet_grid( mode ~ HHS, scales = "free_y")
